Compararison of analytical and artificial neural network models in predicting hot deformation behavior of AISI P20 and interpolation-extrapolation capacity validation

### 2022-11-15 Article.tex
Update Appendix

Conforming to the computing process proposed by Equations (\ref{eq:CR1}-\ref{eq:CR2}), we report hereafter the $180$ coefficients of the ANN-3-15-7-1-sigmoid model used in Section \ref{sec:ANNmodel}.

\begin{equation*}
\w_1^T = \left[
\begin{array}{rrr}
2.2206 & -3.7555 & -6.7246\\ 
-4.8598 & 5.7431 & -5.8538\\ 
2.3099 & 3.3325 & -5.1795\\ 
2.0475 & 0.8006 & -1.4259\\ 
8.8358 & -6.0362 & 0.8226\\ 
-1.2613 & -0.9274 & -2.3725\\ 
-0.3561 & 6.5032 & -10.7573\\ 
-11.7226 & -2.0455 & 1.2248\\ 
3.1066 & 26.5580 & 18.6540\\ 
-0.5150 & -5.6922 & 1.0104\\ 
-6.4755 & 8.4888 & -2.4459\\ 
-1.8791 & -0.5380 & 2.2295\\ 
-6.0206 & 1.2776 & 0.2169\\ 
0.2619 & -4.7974 & -1.1282\\ 
-27.1456 & -0.5327 & -0.5303\\ 
\end{array}\right]
\end{equation*}
\begin{equation*}
\overrightarrow{b}_1 = \left[
\begin{array}{r}
5.9164\\ 
-1.9074\\ 
-2.6837\\ 
-1.0954\\ 
-0.9509\\ 
3.1682\\ 
-4.3964\\ 
0.6343\\ 
-5.0676\\ 
2.0228\\ 
1.1267\\ 
-0.9671\\ 
-0.6263\\ 
2.3110\\ 
-0.3037\\ 
\end{array}\right]
\end{equation*}
\begin{equation*}
\w_2 = \left[
\begin{array}{rrrrrrr}
-0.5783 & 1.2724 & 0.5747 & 0.6449 & -4.2203 & -0.2380 & 0.2591\\ 
-0.4852 & 5.2807 & 0.8888 & -8.2324 & -2.0075 & -0.6474 & -1.0787\\ 
4.4499 & -0.0137 & 0.1657 & 0.3198 & 4.9765 & -1.2503 & 0.8219\\ 
1.7571 & 0.7730 & 0.0208 & -1.3316 & -0.8945 & -0.7284 & -0.1831\\ 
-1.0866 & 0.1330 & -0.8615 & -0.1283 & 0.2218 & -0.1772 & -2.7458\\ 
-0.3925 & 1.3994 & 0.0630 & -1.8397 & -1.1047 & -1.9839 & 0.5767\\ 
-0.2121 & 0.9977 & 1.2028 & -9.6525 & 0.5520 & 0.1062 & -0.0409\\ 
-1.1518 & -1.6402 & -4.1501 & -1.0759 & 0.4749 & -2.8350 & 0.9225\\ 
-1.1453 & -0.2173 & -0.1382 & 0.8264 & -0.5125 & 0.1882 & -0.8654\\ 
-4.3301 & -0.3711 & -7.4305 & 3.5926 & -9.6217 & -1.2375 & 1.6171\\ 
2.3907 & -1.0085 & -0.8828 & -1.1891 & 0.9947 & 1.1178 & -1.0953\\ 
-1.5955 & 1.6313 & 0.4916 & 0.1906 & -1.9216 & -1.4140 & 1.3827\\ 
-1.6985 & 1.4277 & -3.4462 & -8.3777 & -1.2132 & -1.2158 & 2.8512\\ 
-1.9954 & -2.0159 & -8.3455 & -0.5205 & 0.2942 & -1.3337 & 0.2026\\ 
4.3040 & -0.7164 & -1.0859 & 3.4294 & -23.8003 & 12.5859 & 7.3721\\ 
\end{array}\right]
\end{equation*}
\begin{equation*}
\overrightarrow{b}_2 = \left[
\begin{array}{r}
0.7534\\ 
0.9473\\ 
0.6055\\ 
-0.7793\\ 
-1.0305\\ 
-1.5779\\ 
-0.1471\\ 
\end{array}\right]
\end{equation*}
\begin{equation*}
\overrightarrow{w}_3 = \left[
\begin{array}{r}
0.1920\\ 
0.3406\\ 
0.3839\\ 
-0.2880\\ 
1.2047\\ 
-1.4126\\ 
-0.2215\\ 
\end{array}\right]
\end{equation*}
\begin{equation*}
b_3 = 0.1178 
\end{equation*}

>>>>

Conforming to the computing process proposed by Equations (\ref{eq:CR1}-\ref{eq:CR2}), we report hereafter the $180$ coefficients of the ANN-3-15-7-1-sigmoid model used in Section \ref{sec:ANNmodel}.
The weight matrix for the first hidden layer $\w_1$ is a $15\times3$ matrix:
\begin{equation*}
\w_1 = \left[
\begin{array}{rrr}
2.2206 & -3.7555 & -6.7246\\ 
-4.8598 & 5.7431 & -5.8538\\ 
2.3099 & 3.3325 & -5.1795\\ 
2.0475 & 0.8006 & -1.4259\\ 
8.8358 & -6.0362 & 0.8226\\ 
-1.2613 & -0.9274 & -2.3725\\ 
-0.3561 & 6.5032 & -10.7573\\ 
-11.7226 & -2.0455 & 1.2248\\ 
3.1066 & 26.5580 & 18.6540\\ 
-0.5150 & -5.6922 & 1.0104\\ 
-6.4755 & 8.4888 & -2.4459\\ 
-1.8791 & -0.5380 & 2.2295\\ 
-6.0206 & 1.2776 & 0.2169\\ 
0.2619 & -4.7974 & -1.1282\\ 
-27.1456 & -0.5327 & -0.5303\\ 
\end{array}\right]
\end{equation*}
The biases of the first hidden layer $\overrightarrow{b_1}$ is a $15$ components vector:
\begin{equation*}
\overrightarrow{b}_1 = \left[
\begin{array}{r}
5.9164\\ 
-1.9074\\ 
-2.6837\\ 
-1.0954\\ 
-0.9509\\ 
3.1682\\ 
-4.3964\\ 
0.6343\\ 
-5.0676\\ 
2.0228\\ 
1.1267\\ 
-0.9671\\ 
-0.6263\\ 
2.3110\\ 
-0.3037\\ 
\end{array}\right]
\end{equation*}
The weight matrix for the second hidden layer $\w_2$ is a $7\times15$ matrix:
\begin{equation*}
\w_2^T = \left[
\begin{array}{rrrrrrr}
-0.5783 & 1.2724 & 0.5747 & 0.6449 & -4.2203 & -0.2380 & 0.2591\\ 
-0.4852 & 5.2807 & 0.8888 & -8.2324 & -2.0075 & -0.6474 & -1.0787\\ 
4.4499 & -0.0137 & 0.1657 & 0.3198 & 4.9765 & -1.2503 & 0.8219\\ 
1.7571 & 0.7730 & 0.0208 & -1.3316 & -0.8945 & -0.7284 & -0.1831\\ 
-1.0866 & 0.1330 & -0.8615 & -0.1283 & 0.2218 & -0.1772 & -2.7458\\ 
-0.3925 & 1.3994 & 0.0630 & -1.8397 & -1.1047 & -1.9839 & 0.5767\\ 
-0.2121 & 0.9977 & 1.2028 & -9.6525 & 0.5520 & 0.1062 & -0.0409\\ 
-1.1518 & -1.6402 & -4.1501 & -1.0759 & 0.4749 & -2.8350 & 0.9225\\ 
-1.1453 & -0.2173 & -0.1382 & 0.8264 & -0.5125 & 0.1882 & -0.8654\\ 
-4.3301 & -0.3711 & -7.4305 & 3.5926 & -9.6217 & -1.2375 & 1.6171\\ 
2.3907 & -1.0085 & -0.8828 & -1.1891 & 0.9947 & 1.1178 & -1.0953\\ 
-1.5955 & 1.6313 & 0.4916 & 0.1906 & -1.9216 & -1.4140 & 1.3827\\ 
-1.6985 & 1.4277 & -3.4462 & -8.3777 & -1.2132 & -1.2158 & 2.8512\\ 
-1.9954 & -2.0159 & -8.3455 & -0.5205 & 0.2942 & -1.3337 & 0.2026\\ 
4.3040 & -0.7164 & -1.0859 & 3.4294 & -23.8003 & 12.5859 & 7.3721\\ 
\end{array}\right]
\end{equation*}
The biases of the second hidden layer $\overrightarrow{b_2}$ is a $7$ components vector:
\begin{equation*}
\overrightarrow{b}_2 = \left[
\begin{array}{r}
0.7534\\ 
0.9473\\ 
0.6055\\ 
-0.7793\\ 
-1.0305\\ 
-1.5779\\ 
-0.1471\\ 
\end{array}\right]
\end{equation*}
The weight vector for the output layer $\overrightarrow{w}_3$ is a $7$ components vector:
\begin{equation*}
\overrightarrow{w}_3 = \left[
\begin{array}{r}
0.1920\\ 
0.3406\\ 
0.3839\\ 
-0.2880\\ 
1.2047\\ 
-1.4126\\ 
-0.2215\\ 
\end{array}\right]
\end{equation*}
The bias of the output layer $b_3$ is a scalar:
\begin{equation*}
b_3 = 0.1178 
\end{equation*}
